A Wide-Coverage Symbolic Natural Language Inference System

### 2019-07-16 paper2018/paper.tex
minor addition

In this paper, we concentrate on this sort of fine-grained, logical
reasoning. In particular, we present a logic-based system that deals
with many linguistic phenomena \emph{at the same time}. It is the
first systems covering the sections on ellipsis and anaphora in the
FraCaS test suite and has the best coverage and accuracy on the
overall test suite.
% This is listed below; we can let the reader figure it out.
% \begin{itemize}
% \item A two-phase system (rather than a one-phase as described by
%   \citet{bernardy_type_2017}): a) using Haskell as a converter between
%   Grammatical Framework trees and Coq types, b) using various type
%   combinators to reach the desired NL semantics.
% \item The first run of the Anaphora and Ellipsis sections of the
%   FraCaS (based on work by \citet{bernardy_jolli})
%  \item  More coverage than any previous logical approach
%  \item State-of-the-art results in terms of accuracy compared to all
%    previous approaches, for every section of the FraCaS
%   \item Handing of multiple readings
%   \item  Threshold-based interpretation of (some) adjectives plus Linear arithmetic proofs
%   \item New handling of prepositions and adverbs compared to the
%     earlier system in \citet{bernardy_type_2017}, as well as new
%     handling of definitions, enabled by the dynamic semantics system.
%   \item Improvement over the previous treatment of Plurals/Quantifiers
%   \item Big improvement on the comparatives section enabled by
%     handling comparatives using a threshold (BUT one different to the
%     one used for adjectives). Again, the dynamic semantics system is
%     crucial here.
% \end{itemize}

@@

\paragraph{Coq}
Coq is an interactive theorem prover (proof assistant) based on the
calculus of inductive constructions (CiC), i.e.  a lambda calculus
with dependent types.  Coq is a very powerful reasoning engine
that makes it fit for the task of NLI, when the latter is formalized
as theorem proving task. It supports
notably dependent typing and subtyping, which are instrumental in
expressing NL semantics.

@@

\paragraph{Ellipsis} Ellipsis is handled in essentially the same way
as anaphora. This method is made especially straightforward thanks to
using GF syntax trees, which require an explicit argument for each
predicate. Thus, ellipsis are made explicit by the parsing phase. Such
ellptic expressions are handled in the same way as anaphora.
%
For example, in \ref{ex:acd}, the argument of ``did'' is
explicitly marked as an elliptic V2, which we resolve to ``speak'' in
that context.

>>>>

In this paper, we concentrate on this sort of fine-grained, logical
reasoning. In particular, we present a logic-based system that deals
with many linguistic phenomena \emph{at the same time}. It is the
first system covering the sections on ellipsis and anaphora in the
FraCaS test suite and has the best coverage and accuracy on the
overall test suite.
% This is listed below; we can let the reader figure it out.
% \begin{itemize}
% \item A two-phase system (rather than a one-phase as described by
%   \citet{bernardy_type_2017}): a) using Haskell as a converter between
%   Grammatical Framework trees and Coq types, b) using various type
%   combinators to reach the desired NL semantics.
% \item The first run of the Anaphora and Ellipsis sections of the
%   FraCaS (based on work by \citet{bernardy_jolli})
%  \item  More coverage than any previous logical approach
%  \item State-of-the-art results in terms of accuracy compared to all
%    previous approaches, for every section of the FraCaS
%   \item Handing of multiple readings
%   \item  Threshold-based interpretation of (some) adjectives plus Linear arithmetic proofs
%   \item New handling of prepositions and adverbs compared to the
%     earlier system in \citet{bernardy_type_2017}, as well as new
%     handling of definitions, enabled by the dynamic semantics system.
%   \item Improvement over the previous treatment of Plurals/Quantifiers
%   \item Big improvement on the comparatives section enabled by
%     handling comparatives using a threshold (BUT one different to the
%     one used for adjectives). Again, the dynamic semantics system is
%     crucial here.
% \end{itemize}

@@

\paragraph{Coq}
Coq is an interactive theorem prover (proof assistant) based on the
calculus of inductive constructions (CiC), i.e.  a lambda calculus
with dependent types.  Coq is a very powerful reasoning engine
that makes it fit for the task of NLI, when the latter is formalized
as a theorem proving task. It supports
notably dependent typing and subtyping, which are instrumental in
expressing NL semantics.

@@

\paragraph{Ellipsis} Ellipsis is handled in essentially the same way
as anaphora. This method is made especially straightforward thanks to
using GF syntax trees, which require an explicit argument for each
predicate. Thus, ellipsis are made explicit by the parsing phase. Such
ellptic expressions are handled in the same way as anaphora.
%
For example, in \ref{ex:acd} repeated below as \ref{ex:acda},  the argument of ``did'' is
explicitly marked as an elliptic V2, which we resolve to ``speak'' in
that context:

\begin{lingex}
	\item
	\label{ex:acda}
	\textbf{P1}	Bill spoke to everyone that John did [elliptic V2].\\
	\textbf{P2}	John spoke to Mary.\\
	\textbf{Q} 	Did Bill speak to Mary?\\
	\textbf{H} 	Bill spoke to Mary. \\ \textbf{Label:	Yes} [FraCas 173]
\end{lingex}
